Supplementary Materials for: ``Well-Designed Environmental Markets Enable Large-Scale Marine Conservation''

### 2019-10-22 docs/Markets_Conservation_revised_Oct22.tex
Added changes by Chris

% Place your abstract within the special {sciabstract} environment.
\begin{abstract}
While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have yet to implement large-scale Marine Protected Areas in their own waters. When a country closes a large fraction of its waters to fishing, it stands to lose significant fishery revenue. While this may be more-than-made-up-for through spillover, these benefits typically accrue to other countries or the high seas. We show that careful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than relegate, large scale marine conservation. By combining a model of cross-country trading of rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that two market design features are pivotal to encouraging such conservation. First, only when trading of fishing rights across countries is allowed, can a conservation-minded country capture the economic spillover benefits of their conservation actions. Second, the allocation of rights to countries must not be watered-down over time by a country's conservation efforts; for example, a country's annual allocation of rights should depend on the size of the fish stock in their waters, not on how hard it has fished. Overall, these results provide a template for how to incentivize countries to engage in large-scale marine conservation within a market-based setting.
\end{abstract}

@@

Recognizing the need to protect marine biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world by protecting 30\% of the oceans \cite{oleary_2016,dinerstein_2019}, and that large portions of these will be entirely no-take \cite{sala_2017,sala_2018}. While most marine protected areas (MPAs) implemented to date have been small, it is widely-recognized that to meet these goals, very large MPAs must also be part of the strategy. But would any country rationally close 30\%, 80\% or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area? At first glance, the answer is probably ``no''. Losing this important source of revenue would cripple many fishing-dependent economies, particularly the Pacific Island nations who are viewed as viable candidates for large closures \cite{mcleod_2019}. On the other hand, the closure may generate substantial ``spillover'' of larvae and adult fish \cite{ramesh_2019,hernndez_2019} and other benefits into adjacent waters which could, in principle, offset these losses. The problem with this argument is that for very large MPAs, these spillover benefits could accrue to other nations and the high seas \cite{agardy_2018}, with no obvious mechanism for the conserving country to recoup them. A viable solution may lie in international fishing effort markets, where nations trade the right to fish with each other. The design and effectivness of fishing effort markets for fisheries management have been explored before \cite{havice_2010,havice_2013}, but little attention has been given to the role that markets can play in conservation. Here, we will show how fishing effort markets can be designed (if new) or modified (if already existing) to incentivize implementation of large-scale marine protected areas.

We are motivated by a real-world but relatively understudied institution called the Parties to the Nauru Agreement (PNA). The PNA is a coalition of nine Pacific island nations that collectively manages tuna purse seine fishing in its members' waters (Fig. \ref{fig:PNA_map}) \cite{havice_2013,aqorau_2018}. These waters account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}. The PNA manages this tuna purse seine fishery using a vessel-day scheme (VDS) where total annual fishing effort is capped at around 45,000 vessel-days. Vessel-days are allocated across the nine nations, which then lease them to fishing vessels. A vessel-day grants a fishing vessel the right to fish for 24 hours within one of the nine Exclusive Economic Zones (EEZs) within the PNA. Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's GDP. In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}. In 2015, Kiribati, a PNA member, created the Phoenix Islands Protected Area, one of the largest protected areas on earth (408,250 km\textsuperscript{2}), and Palau will close 80\% of its national waters to fishing by December 2020. We draw from the PNA's market-based approach to managing tuna fisheries and build on it to show how the market can be designed to incentivize conservation.

Not all market-based approaches to environmental management are created equal. A pervasive finding across a range of natural resources is that features of markets, such as the allocation of rights, can have implications for the market's functioning \cite{libecap_1989}. In the context of fishing effort markets, we find that two market design features are pivotal in determining the incentives for large-scale marine conservation: trading and allocation rules. But why would these design features of a fisheries market affect the incentives for conservation? Consider the incentives for a country to close 100\% of its waters. Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of neighboring countries. If the conserving country could trade the rights to catch the fish that spillover, other countries would likely buy them, offsetting the costs of not fishing its own waters. But if the conserving country was not allowed to lease these rights, then it would lose all of its fishing revenue. The rules for how fishing rights are allocated across countries are equally important. Suppose rights are allocated each year based on the previous year's fishing effort: the more a country fishes, the more it gets allocated the next year. This would clearly disadvantage a conservation-minded country and, in fact, might reward undesirable behavior. In the following section, we will show how trading and allocation rules can shape the incentives that may facilitate or hinder large-scale conservation. We will then make use of vessel-tracking data to analyze a real-world case of large-scale marine conservation under fishing effort markets.

@@

To examine how market design incentivizes or punishes large-scale conservation, we develop a 10-country spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA nations and the high seas. Countries 1 to 9 represent the PNA countries, which operate under a vessel-day scheme where vessel-days are capped for each country and closely tracked. ``Country'' 10 represents the high seas, where fishing days are unregulated and determined by prevailing economic conditions. We examine the effects of large-scale conservation in a single country (Country 1) under markets with and without trading between countries. In all cases, we solve the bioeconomic model for the equilibrium vessel-day price, fishing effort redistribution, and fish stock that would be expected to occur in the market. We quantify the change in revenue to Country 1 and compare each scenario to a benchmark scenario without any conservation action. We simulate these outcomes across a range of reserve sizes and assumptions about within-country stock movement (see the Methods section for details).

We first simulate a fishery where trading between countries is not allowed. This represents the status quo of any nation unilaterally engaging in large-scale conservation. Intuitively, we find that a spatial closure in Country 1 will always result in a loss in revenues to Country 1 (Fig. \ref{fig:PNA_model}A). Higher within-country stock movement ($\theta$ = 0 implies no within-country movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1. The closure-to-cost ratio for any reserve size is greater than 1:1 when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues. Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving country (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig. S1). When countries cannot trade, the costs of conservation are incurred by Country 1, but the benefits are received by the eight other countries (revenues increase between 0\% and 6\% each; Fig. S2) and the high seas. This benchmark simulation highlights the misalignment of incentives, where a conservation-minded country incurs large costs and provides public benefits to other nations with no mechanism for recouping these benefits.

How would trading between countries change these results? We simulate the same fishery, but now allow for vessel-days to be traded across countries (as is the case for the PNA). As before, a closure in Country 1 lowers the value of vessel-days in that country (because the fishable water shrinks). But increased biomass in other countries causes their vessel day prices to increase. As a result, vessel-days from Country 1 are traded to Countries 2 to 9, until prices equalize across countries (Fig. S3). Under this market design, revenue losses are less than 1\%, compared to the base case with no reserve (Fig. \ref{fig:PNA_model}B; note that the vertical axis now only ranges from 0 to 0.8\% instead of from 0 to 100\% as in Fig. \ref{fig:PNA_model}A). With trading, the relative revenue drop will always be smaller than the relative effort drop, and the opposite is observed when there is no trading (Fig. S4). Overall, this shows that 88\% to 99\% of the costs of conservation can be avoided if markets are designed to allow trading (Fig. \ref{fig:PNA_model}C).

We have shown that trading significantly reduces the costs of conservation. However, a new question arises. How should rights be re-allocated every year once a country starts closing its waters to fishing? Customarily, the allocation of fishing effort rights is a formula that combines historical fishing effort and biomass in a country's waters \cite{havice_2013}. We test a range of allocation rules that weigh effort ($\alpha$) and biomass ($1 - \alpha$) differently as the basis for ongoing rights allocation. We simulate a fishery operating with closures for 50 years and compare the resulting revenues to a fishery without any closures. We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement (Fig. \ref{fig:allocation_cost_plot}). However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation. This result implies that if allocation is based purely on the biological features of a stock (\emph{e.g.} the biomass within a nation's waters), and not on fishing effort, the incentives for conservation are sustained through time.

@@

Consistent with our models' prediction, after PIPA was implemented, displaced vessels relocated largely outside of Kiribati, and into other PNA countries' waters (Fig \ref{fig:fishing_raster_diff} and Figs. S6). Indeed, from 2014 to 2015, displaced vessels spent 2,115 fewer vessel-days (a 25\% reduction) in Kiribati, and 2,298 fewer vessel-days in PNA waters (a 17 \% reduction; Fig. \ref{fig:empirical}). On the other hand, non-displaced vessels spent 4,656 additional days in Kiribati during 2015, and an additional 9,598 vessel-days in PNA waters. By 2018, we observe a net decrease of vessel-days within Kiribati, from 12,671 in 2014 to just 7,677 in 2018, with displaced vessels driving the decrease (Fig. \ref{fig:empirical}A). However, aggregate effort at the PNA-level remains relatively constant and we do not observe a ``fishing the line'' effect (Fig S7). The reduction in effort to Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters, just as the model predicted.

The decrease of vessel-days in Kiribati could be alternatively (or jointly) explained by changes in oceanographic conditions that drive distribution of target species and fishing vessels. For example, as El Niño events develop, tuna species are known to shift longitudinally across PNA waters, causing vessels to redistribute \cite{aqorau_2018,hanich2018unraveling}. However, the total decrease that we observe for Kiribati in Fig. \ref{fig:empirical} is driven by the relocation of vessels that once fished within PIPA, not the entire fleet. One could argue that differences in vessel characteristics between displaced and non-displaced vessels may influence their ability to redistribute or take advantage of different oceanographic conditions in Kiribati. For example, on average, displaced vessels have smaller crew sizes, more engine power, and are larger than non-displaced vessels (Table S2, Fig. S5). However, displaced vessels gradually reduce their time spent in PNA waters too.

As predicted by our theoretical model, the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's water without large revenue losses. Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig. \ref{fig:empirical}C). The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati from 2014 to 2016 (Fig. \ref{fig:empirical}D). But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%). This supports a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig. S4). At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig. S8), despite the PIPA closure.

Our findings may help inform management and implementation of existing and upcoming MPAs in the PNA. In January 2020, Palau will close nearly 80\% of its EEZ to commercial fishing to create the Palau National Marine Sanctuary (PNMS): the 14\textsuperscript{th} largest protected area in the world (Fig. \ref{fig:PNA_map}). Vessel-tracking data (2012 to 2018) shows that the proposed PNMS boundaries contain 65.6 $\pm$ 0.08\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 82.2 $\pm$ 0.08\% ($\pm$ 1SD) of purse seine vessel-days (tradable; Fig. S10-S11).

@@

There are, however, a series of important considerations to take into account. Firstly, in our study only one of the countries considers the implementation of a protected area. However, an interesting extension would be that of cooperative conservation. In that setting, a group of countries could coordinate on an optimized, large-scale strategic closure -perhaps using vessel-day trading as a means of compensation- in a manner similar to the model above. Future research could explore the role of heterogeneous costs and benefits between countries, and the way in which these can shape conservation outcomes in a market-based setting. A second consideration is that of the role that the high seas play: environmental markets require secure property rights, which are lacking in the high seas \cite{crespo_2019}. Any spillover from into the high seas could potentially be eroded by the prevailing open access conditions. Therefore, a conservation-minded nation has no mechanism to capture the benefits provided to the high seas, highligting the importance of empowering high seas governance and transboundary cooperation \cite{aqorau_2018,crespo_2019}.

@@

We can then compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution. Non-displaced vessels serve as a plausible control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as El Niño \cite{hanich2018unraveling,aqorau_2018}.

@@

>>>>

% Place your abstract within the special {sciabstract} environment.
\begin{abstract}
While it is commonly agreed that marine conservation should expand dramatically around the world, most countries have yet to implement large-scale Marine Protected Areas in their own waters. When a country closes a large fraction of its waters to fishing, it stands to lose significant fishery revenue. While this may be more-than-made-up-for through spillover, these benefits typically accrue to other countries or the high seas. We show that careful design of cross-country rights-based approaches to fisheries can actually incentivize, rather than hinder, large scale marine conservation. By combining a model of cross-country trading of rights with vessel-level tracking data before and after a large-scale conservation action is implemented, we show that two market design features are pivotal to encouraging such conservation. First, only when trading of fishing rights across countries is allowed, can a conservation-minded country capture the economic spillover benefits of their conservation actions. Second, the allocation of rights to countries must not be watered-down over time by a country's conservation efforts; for example, a country's annual allocation of rights should depend on the size of the fish stock in their waters, not on how hard it has fished. Overall, these results provide a template for how to incentivize countries to engage in large-scale marine conservation within a market-based setting.
\end{abstract}

@@

Recognizing the need to protect marine biodiversity and ecosystem services, various international bodies have committed to dramatically expand marine protection around the world by protecting 30\% of the oceans \cite{oleary_2016,dinerstein_2019}, and that large portions of these will be entirely no-take \cite{sala_2017,sala_2018}. While most marine protected areas (MPAs) implemented to date have been small, it is widely-recognized that to meet these goals, very large MPAs must also be part of the strategy. But would any country rationally close 30\%, 80\% or even 100\% of its waters to fishing if this means losing all fishing revenue from within the closed area? At first glance, the answer is probably ``no''. Losing this important source of revenue would cripple many fishing-dependent economies, particularly the Pacific Island nations who are viewed by many as viable candidates for large closures \cite{mcleod_2019}. On the other hand, the closure may generate substantial ``spillover'' of larvae and adult fish \cite{ramesh_2019,hernndez_2019} and other benefits into adjacent waters which could, in principle, offset these losses. The problem with this argument is that for very large MPAs, these spillover benefits could accrue to other nations and the high seas \cite{agardy_2018}, with no obvious mechanism for the conserving country to recoup them. A viable solution may lie in international fishing effort markets, where nations trade the right to fish. The design and effectivness of fishing effort markets for fisheries management have been explored before \cite{havice_2010,havice_2013}, but little attention has been given to the role these markets can play in conservation. Here, we will show how fishing effort markets can be designed (if new) or modified (if already existing) to incentivize implementation of large-scale marine protected areas.

We are motivated by a real-world but relatively understudied institution called the Parties to the Nauru Agreement (PNA). The PNA is a coalition of nine Pacific island nations that collectively manages tuna purse seine fishing in its members' waters (Fig. \ref{fig:PNA_map}) \cite{havice_2013,aqorau_2018}. These waters account for 14.5 million km\textsuperscript{2} (an area four times larger than the continental US), and over 60\% of skipjack tuna catch in the Western Central Pacific \cite{havice_2013}. The PNA manages this tuna purse seine fishery using a vessel-day scheme (VDS) where total annual fishing effort is capped at around 45,000 vessel-days. Vessel-days are allocated across the nine nations, which then lease them to (mostly foreign) fishing vessels. A vessel-day grants a fishing vessel the right to fish for 24 hours within one of the nine Exclusive Economic Zones (EEZs) within the PNA. Member nations derive enormous benefits from leasing these fishing rights to foreign fleets, in some cases exceeding half of a country's GDP (XXX). In addition to highly productive tuna fisheries, the PNA waters provide a wealth of ecosystem benefits, hence the focus on large-scale conservation efforts in the region \cite{mcleod_2019}. In 2015, Kiribati, a PNA member, created the Phoenix Islands Protected Area, one of the largest protected areas on earth (408,250 km\textsuperscript{2}), and Palau will close 80\% of its national waters to fishing by December 2020. We draw from the PNA's market-based approach to managing tuna fisheries and build on it to show how the market can be designed to incentivize conservation.

Not all market-based approaches to environmental management contain the same conservation incentives. A pervasive finding across a range of natural resources is that features of markets, such as the allocation of rights, can have implications for the market's functioning \cite{libecap_1989}. In the context of fishing effort markets, we find that two market design features are pivotal in determining the incentives for large-scale marine conservation: trading and allocation rules. But why would these design features of a fisheries market affect the incentives for conservation? Consider the incentives for a country to close 100\% of its waters. Such a closure would surely benefit other countries through the spillover of fish from the protected area to the waters of neighboring countries. If the conserving country could lease the rights to that spillover to adjacent countries, this could offset the foregone fisheries revenue. But if the conserving country was not allowed to lease these rights, then it would lose all of its fishing revenue. The rules for how fishing rights are allocated across countries are equally important. Suppose rights are allocated each year based on the previous year's fishing effort: the more a country fishes, the more it gets allocated the next year. This would clearly disadvantage a conservation-minded country and, in fact, might reward undesirable behavior. In the following section, we will show how trading and allocation rules can shape the incentives that may facilitate or hinder large-scale conservation. We will then make use of vessel-tracking data to analyze a real-world case of large-scale marine conservation under fishing effort markets.

@@

To examine how market design incentivizes or punishes large-scale conservation, we develop a 10-country spatial bioeconomic model that mirrors the strategies and spatial connections among the nine PNA nations and the high seas. Countries 1 to 9 represent the PNA countries, which operate under a vessel-day scheme where vessel-days are capped for each country and closely tracked. ``Country'' 10 represents the high seas, where fishing days are unregulated and determined by prevailing economic conditions. We examine the effects of large-scale conservation in a single country (Country 1) under markets with and without trading between countries. In all cases, we solve the bioeconomic model for the equilibrium vessel-day price, fishing effort redistribution across countries, and fish stock that would be expected to occur in the market. We quantify the change in revenue to Country 1 and compare each scenario to a benchmark scenario without any conservation action. We simulate these outcomes across a range of reserve sizes and assumptions about within-country stock movement (see the Methods section for details).

We first simulate a fishery where trading between countries is not allowed. This represents the status quo of any nation unilaterally engaging in large-scale conservation. Intuitively, we find that a spatial closure in Country 1 will always result in a loss in revenues to Country 1 (Fig. \ref{fig:PNA_model}A). Higher within-country stock movement ($\theta$ = 0 implies no within-country movement and $\theta = 1$ implies that fish are well-mixed within the fishing season) allows vessels to harvest the stock within the remaining open area, lowering the cost to Country 1. The closure-to-cost ratio for any reserve size is greater than 1:1 (XXX Why) when stock movement is low (\emph{i.e.} $\theta < 0.2$), implying that a 30\% closure would result in at least a 30\% loss in revenues. Even for a highly mobile stock where fish can move in and out of the reserve, a spatial closure reduces the amount of biomass that is available for harvest in the conserving country (\emph{i.e.} biomass outside the reserve), which reduces vessels' willingness to pay to fish in such waters (Fig. S1). When countries cannot trade, the costs of conservation are incurred by Country 1, but the benefits are received by the eight other countries (revenues increase between 0\% and 6\% each; Fig. S2) and the high seas. This benchmark simulation highlights the misalignment of incentives, where a conservation-minded country incurs large costs and provides public benefits to other nations with no mechanism for recouping these benefits.

How would trading between countries change these results? We simulate the same fishery, but now allow for vessel-days to be traded across countries (as is the case for the PNA). As before, a closure in Country 1 lowers the value of vessel-days in that country (because the fishable water shrinks). But increased biomass in other countries causes their vessel day prices to increase. As a result, vessel-days from Country 1 are traded to Countries 2 to 9, until prices equalize across countries (Fig. S3). Under this market design, revenue losses to Country 1 are less than 1\%, compared to the base case with no reserve (Fig. \ref{fig:PNA_model}B; note that the vertical axis now only ranges from 0 to 0.8\% instead of from 0 to 100\% as in Fig. \ref{fig:PNA_model}A). With trading, the relative revenue drop will always be smaller than the relative effort drop, and the opposite is observed when there is no trading (Fig. S4). Overall, this shows that 88\% to 99\% of the costs of conservation can be avoided if markets are designed to allow trading (Fig. \ref{fig:PNA_model}C).

We have shown that trading significantly reduces the costs of conservation. However, a new question arises. How should rights be re-allocated every year once a country starts closing its waters to fishing? Customarily, the allocation of fishing effort rights is a formula that combines historical fishing effort and biomass in a country's waters \cite{havice_2013}. We test a range of allocation rules that weigh effort ($\alpha$) and biomass ($1 - \alpha$) differently as the basis for ongoing rights allocation. We simulate a fishery operating with closures for 50 years and compare the resulting revenues to a fishery without any closures. We find that when allocation is based on historical effort only (\emph{i.e.} $\alpha = 1$), implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement (Fig. \ref{fig:allocation_cost_plot}). However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses as low as 0.1\% to 0.7\%, essentially eliminating the costs of conservation. This result implies that if allocation is based purely on the biological features of a stock (\emph{e.g.} the biomass within a nation's waters), and not on fishing intensity, the incentives for conservation can be sustained through time.

@@

Consistent with our model's prediction, after PIPA was implemented, displaced vessels relocated largely outside of Kiribati, and into other PNA countries' waters (Fig \ref{fig:fishing_raster_diff} and Figs. S6). Indeed, from 2014 to 2015, displaced vessels spent 2,115 fewer vessel-days (a 25\% reduction) in Kiribati, and 2,298 fewer vessel-days in PNA waters (a 17 \% reduction; Fig. \ref{fig:empirical}). On the other hand, non-displaced vessels spent 4,656 additional days in Kiribati during 2015, and an additional 9,598 vessel-days in PNA waters. By 2018, we observe a net decrease of vessel-days within Kiribati, from 12,671 in 2014 to just 7,677 in 2018, with displaced vessels driving the decrease (Fig. \ref{fig:empirical}A). However, aggregate effort at the PNA-level remains relatively constant and we do not observe a ``fishing the line'' effect (Fig S7). The reduction in effort to Kiribati and constant effort at the PNA-level suggest that trading facilitated redistribution of effort within PNA waters, just as the model predicted.

The decrease of vessel-days in Kiribati could be alternatively (or jointly) explained by changes in oceanographic conditions that drive distribution of target species and fishing vessels. For example, as El Ni\~no events develop, tuna species are known to shift longitudinally across PNA waters, causing vessels to redistribute \cite{aqorau_2018,hanich2018unraveling}. However, the total decrease that we observe for Kiribati in Fig. \ref{fig:empirical} is driven by the relocation of vessels that once fished within PIPA, not by the entire fleet. One could argue that differences in vessel characteristics between displaced and non-displaced vessels may influence their ability to redistribute or take advantage of different oceanographic conditions in Kiribati. For example, on average, displaced vessels have smaller crew sizes, more engine power, and are larger than non-displaced vessels (Table S2, Fig. S5). However, displaced vessels gradually reduce their time spent in PNA waters.

As predicted by our model, the implementation of PIPA resulted in a decrease in fishing effort within Kiribati's water without large revenue losses. Kiribati's reported revenue increased from US\$127.3 million in 2014 to US\$148.8 million in 2015, before decreasing to US\$118.3 million in 2016 (Fig. \ref{fig:empirical}C). The increase and subsequent decrease in revenues matches the vessel-day patterns observed for Kiribati from 2014 to 2016 (Fig. \ref{fig:empirical}D). But, critically, the drop in revenue in 2016 (20\%) is smaller than the drop in VDS effort (35\%). This supports a key prediction of our model: with trading, the relative revenue drop will always be smaller than the relative effort drop but, without trading, the opposite relationship would hold (Fig. S4). At the PNA level, total revenues showed a net increase of \$64.7 and \$28 million USD for 2015 and 2016 respectively (Fig. S8), despite the PIPA closure.

Our findings may help inform management and implementation of existing and upcoming MPAs in the PNA. In January 2020, Palau will close nearly 80\% of its EEZ to commercial fishing to create the Palau National Marine Sanctuary (PNMS): the 14\textsuperscript{th} largest protected area in the world (Fig. \ref{fig:PNA_map}). Vessel-tracking data (2012 to 2018) shows that the proposed PNMS boundaries have historically contained 86 $\pm$ 5.30\% ($\pm$ 1SD) of longline vessel-days (non-tradable) and 91.3 $\pm$ 5.03\% ($\pm$ 1SD) of purse seine vessel-days (tradable) in Palauan waters (Fig. S10-S11).

@@

There are, however, a series of important considerations to take into account. First, in our study only one of the countries considers the implementation of a protected area. However, an interesting extension would be that of cooperative conservation. In that setting, a group of countries could coordinate on an optimized, large-scale strategic closure -perhaps using vessel-day trading as a means of compensation- in a manner similar to the model above. Future research could explore the role of heterogeneous costs and benefits between countries, and the way in which these can shape conservation outcomes in a market-based setting. A second consideration is that of the role that the high seas play: environmental markets require secure property rights, which are lacking in the high seas \cite{crespo_2019}. Any spillover into the high seas could potentially be eroded by the prevailing open access conditions. Therefore, a conservation-minded nation has no mechanism to capture the benefits provided to the high seas, highligting the importance of empowering high seas governance and transboundary cooperation \cite{aqorau_2018,crespo_2019}. Finally, our work focuses on fisheries and large-scale conservation, but the framework could potentially be expanded and applied to other systems and natural resources. For example, similar mechanisms could be implemented in markets for tradable water rights \cite{rosegrant_1994} or game hunting \cite{hutton_2003} where secure property rights and the presence of a market may incentivise users to conserve the resource in question.

@@

We can then compare the footprint of displaced and non-displaced vessels before and after the implementation of PIPA to better understand the effort redistribution. Non-displaced vessels serve as a plausible control group that was not subject to a spatial closure but might have redistributed in response to changing environmental conditions, such as El Ni\~no \cite{hanich2018unraveling,aqorau_2018}.

@@

\subsection{Data availability}

The data and code that support the findings of this study are available on \href{https://github.com/jcvdav/MPA_displacement}{GitHub}

### 2019-10-22 docs/Supplementary_materials.tex
Added changes by Chris

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{l|r|l}
\hline
Parameter & Value & Source\\
\hline
MSY & 1.875600e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$B_{msy}$ & 1.628000e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
K & 6.876526e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$B_c/B_{msy}$ & 0.51 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$C_{now}$ & 1.679444e+06 & Catches from WCPFC Stock Assessment\\
\hline
$B_{now}$ & 3.507028e+06 & Current Biomass (2012 - 2015 average)\\
\hline
$r$ & 0.57 & From FishBase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
\hline
$\beta$ & 1.3 & Standard\\
\hline
p & 1100 & Mean between Thailand and Japan values (Value of WCPFC-CA Tuna Fisheries 2017 Report)\\
\hline
q & 3.420000e-05 & Estimated so that efforts match catches given biomass and vessel-day prices\\
\hline
c & 1800 & Estimated to match cost and revenue structures\\
\hline
f & 0.1 & Biomass is equally distributed between countries\\
\hline
\end{tabular}}
\end{table}

@@

\caption{\label{tab:balance_table}Mean values on observable characteristics by vessel for displaced (n = 64), and non-displaced vessels (n = 254). Numbers in parentheses indicate standard deviation. The last column contains the difference in means (t-scores), with asterisks inicating significant differences as indicated by a two-tailed t-test (* p < 0.1; ** p< 0.05; *** p < 0.01).}
\centering
\begin{tabular}{l|l|l|l}
\hline
Characteristic & Displaced & Non-displaced & Difference\\
\hline
Crew size (n) & 26.38 (3.94) & 30.46 (6.25) & 4.08 (6.49) ***\\
\hline
Engine Power (KW) & 2983.6 (558.76) & 2559.89 (588.28) & -423.71 (-5.36) ***\\
\hline
Length (m) & 74.23 (9.71) & 68.97 (8.42) & -5.25 (-3.97) ***\\
\hline
Tonnage (GT) & 1718.14 (653.38) & 1383.41 (533.56) & -334.73 (-3.79) ***\\
\hline
\end{tabular}
\end{table}

\section{Data and code availability}

Raw data and code used in this work are available on \href{https://github.com/jcvdav/MPA_displacement}{github}.

@@

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_cty_year.pdf}
	\caption{\label{fig:all_PS_VDS_cty_year}Annual country-level vessel-days for all PNA countries by 313 tuna purse seiners.}
\end{figure}

@@

>>>>

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{l|r|l}
\hline
Parameter & Value & Source\\
\hline
MSY & 1.875600e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$B_{msy}$ & 1.628000e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
K & 6.876526e+06 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$B_c/B_{msy}$ & 0.51 & 50th percentile from MSY in Table 8 of WCPFC Stock Assessment\\
\hline
$C_{now}$ & 1.679444e+06 & Catches from WCPFC Stock Assessment\\
\hline
$B_{now}$ & 3.507028e+06 & Current Biomass (2012 - 2015 average)\\
\hline
$r$ & 0.57 & From FishBase: Prior r = 0.57, 95 CL = 0.41 - 0.78\\
\hline
$\beta$ & 1.3 & Standard \cite{costello_2016}\\
\hline
p & 1100 & Mean between Thailand and Japan values (Value of WCPFC-CA Tuna Fisheries 2017 Report)\\
\hline
q & 3.420000e-05 & Estimated so that efforts match catches given biomass and vessel-day prices\\
\hline
c & 1800 & Estimated to match cost and revenue structures\\
\hline
f & 0.1 & Biomass is equally distributed between countries\\
\hline
\end{tabular}}
\end{table}

@@

\caption{\label{tab:balance_table}Mean values on observable characteristics by vessel for displaced (n = 64), and non-displaced vessels (n = 254). Numbers in parentheses indicate standard deviation. The last column contains the difference in means (t-scores), with asterisks inicating significant differences as indicated by a two-tailed t-test (* p $<$ 0.1; ** p $<$ 0.05; *** p $<$ 0.01).}
\centering
\begin{tabular}{l|l|l|l}
\hline
Characteristic & Displaced & Non-displaced & Difference\\
\hline
Crew size (n) & 26.38 (3.94) & 30.46 (6.25) & 4.08 (6.49) ***\\
\hline
Engine Power (KW) & 2983.6 (558.76) & 2559.89 (588.28) & -423.71 (-5.36) ***\\
\hline
Length (m) & 74.23 (9.71) & 68.97 (8.42) & -5.25 (-3.97) ***\\
\hline
Tonnage (GT) & 1718.14 (653.38) & 1383.41 (533.56) & -334.73 (-3.79) ***\\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_cty_year.pdf}
	\caption{\label{fig:all_PS_VDS_cty_year}Annual country-level vessel-days for all PNA countries by 318 tuna purse seiners.}
\end{figure}

@@

\bibliography{references}
\bibliographystyle{nature}
